\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I first want to thank my supervisor Dr. Rachel Crespo-Otero. From when I first interviewed for the position on Skype from a hostel in Colombia, I knew that I wanted to work with her, and I haven't once regretted my decision. She has been the best supervisor I could have asked for, and working with her has been a pleasure. I have learned much from her outstanding scientific abilities and it has been a privilege to be her first PhD student. I appreciate the space that she has given me to explore my own ideas and interests, whilst always being available to discuss any topic at all. The last three years have flown by and I am sad that it is all over. 

I would like to thank Miguel Rivera, who since joining the group has become a great colleague and friend. The last three years with my computational chemistry colleagues, Etienne, Shaima, Fu, Bob, Matteo, Ljiljana, have been a great experience and I thank them for putting up with my habits and bossy traits! I thank my PhD Panel members Prof. Tony Vlcek and Dr. Greg Chass for their interest, discussions and ideas for the project. Thank you to Dr. Devis Di Tommaso for all the help, in particular in molecular dynamics. I would like to thank Prof. Mario Barbatti for his hospitality and scientific expertise when I visited his group in Marseille in June 2018.

The support from my family has been constant during the last three years. My parents have always encouraged me, offering blind optimism that I could solve whatever problem I had, whilst constantly stating they had ``absolotely no idea" what I was doing (something to do with excited atoms). In particular I want to thank my sister, who put up with me as a flatmate during my first two years in London. Her support (mostly financial) will never be forgotten, and will (someday) be repaid. Greg, I like your sheets. 

Finally, I couldn't have done this without my girlfriend Colombine and it is to you I owe the most. Your love, support, and enthusiasm have made this process so easy, even with us living in different countries. Thank you for always being there, always believing in me, and making things so simple. 
