\chapter*{Statement of Originality}
\addcontentsline{toc}{chapter}{Statement of Originality}
I, Michael Dommett, confirm that the research included within this thesis is my own work or that where it has been carried out in collaboration with, or supported by others, that this is duly acknowledged below and my contribution indicated. Previously published material is also acknowledged below.
I attest that I have exercised reasonable care to ensure that the work is original, and does not to the best of my knowledge break any UK law, infringe any third party's copyright or other Intellectual Property Right, or contain any confidential material.
I accept that the College has the right to use plagiarism detection software to check the electronic version of the thesis.
I confirm that this thesis has not been previously submitted for the award of a degree by this or any other university.
The copyright of this thesis rests with the author and no quotation from it or information derived from it may be published without the prior written consent of the author.
\newline
\newline
w
Signature: Michael Dommett 
Date:
\newline
\newline
Details of collaboration and publications:
\begin{enumerate}
    \item \textbf{M.Dommett} and R. Crespo-Otero, \textit{Phys. Chem. Chem. Phys.}, 2017, \textbf{19}, 2409-2416
    \item \textbf{M. Dommett}, M. Rivera and R. Crespo-Otero, \textit{J. Phys. Chem. Lett.}, 2017, 6148-6153
    \item L. del Olmo\textsuperscript{$\dag$}, \textbf{M. Dommett}\footnote[2]{Equal Contribution}, I. H. Oevreeide, A. Walsh, D. Di Tommaso and R. Crespo-Otero, \textit{J. Mater. Chem. A}, 2018, \textbf{6}, 24965-24970
     \item M. Rivera, \textbf{M. Dommett}  and R. Crespo-Otero, \textit{doi.org/10.26434/chemrxiv.7364768.v1}, 2018, 1-38, \textit{Under Review}
     
    \item \textbf{M.Dommett}, M. Rivera, M. T. Hollis-Smith, R. Crespo-Otero, Connecting Crystal Structure and Chromophore Design, \textit{In Preparation}
    
    \item M. Cirulli, E. Salvadori, Z.-H. Zhang, \textbf{M. Dommett}, F. Tuna, H. Bamberger, R. Crespo-Otero, J. van Slageren. S. Goldup and M. Roessler, Tuning the Magnetic Anisotropy of Cobalt(II) Complexes through Peripheral Ligand Modifications: Rotaxane-based Single-Ion Magnets, \textit{In Preparation}

\end{enumerate}